\acknowledgments

This thesis would never have been possible without the guidance of my supervisor, support of my family and help from my friends.

First and foremost, I am heartily thankful to  my supervisor, Prof. Dit-Yan Yeung, for his excellent guidance, caring help, and meticulous comments on my research writing. As a real model, Prof. Yeung have shown me how to be a rigorous researcher, a passionate teacher, and a responsible person. % He has paid much attention to helping me on English writing. 

I would like to show my appreciation for the thesis committee members, Prof. Irwin King (from Department of Computer Science and Engineering, The Chinese University of Hong Kong), Prof. Weichuan Yu (from Department of Electronic and Computer Engineering, The Hong Kong University of Science and Technology), Prof. Nevin L. Zhang, Prof. James T. Kwok, and Prof. Dit-Yan Yeung, for their insightful comments and encouraging words. I am also grateful to Prof. Raymond Wong and Prof. Qiang Yang for their invaluable suggestions on my research.

I would like to thank the members of Prof. Yeung's research group, including Wu-Jun Li, Yang Ruan, Yu Zhang, Jingni Chen, Craig Yu, Tony Ho, Emprise Chan, Zhi-Yang Wang, Nai-Yan Wang, and Jie Zhou. Many thanks to the members of the Artificial Intelligence Lab, including Bin Cao, Nathan Liu, Evan Xiang, Vincent Zheng, Sinno Pan, Chung Lee, Tengfei Liu, Weike Pan, Ning Ding, and Haodi Zhang. Thanks to the visiting members of our lab, including Yan-Ming Zhang, Guoqiang Zhong, Deming Zhai, and Li Pu. In addition, I am grateful to the mentors during my visiting to Microsoft Research Asia, including Jian-Tao Sun and Gang Wang. The friendship, collaboration, and discussion with these friends have made my research and life not only meaningful but also colorful.


Last but not least, I would like to thank my family for supporting and encouraging me throughout my study in Hong Kong. Especially, I am grateful to my wife, Ning Zhu, who has always been right behind me whenever and wherever. I would also like to thank my daughter, Joy Zhen, for her sweet smile which brings happiness and delight to the whole family. My love for all of you is beyond words. 

\endacknowledgments

%First and foremost, I would like to thank my supervisor, Prof. Dit-Yan Yeung, for his support throughout my PhD study at the HKUST. Without his guidance, encouragement, and kindness, this thesis would never have been possible.
%
%I would like to thank my thesis committee members, Prof. Eric Xing (from Machine Learn- ing Department, Carnegie Mellon University), Prof. Mike Ka Pui So (from Department of In- formation Systems, Business Statistics and Operations Management, HKUST), Prof. Nevin L. Zhang, Prof. Qiang Yang, and Prof. Dit-Yan Yeung, for their insightful comments and suggestions.
%I would like to thank the members of Prof. Yeung’s group for their friendship, encourage- ment, support and collaboration, such as Gang Wang, Guang Dai, Chris Kui Jia, Zhihua Zhang, Wu-Jun Li, Yang Ruan, Jingni Chen, Yi Zhen, Craig Yu, Tony Ho, Emprise Chan, Yan-Ming Zhang, Guoqiang Zhong, and Deming Zhai. My many friends at the HKUST have given me an unforgettable memory of both research and everyday life. They are: Bin Cao, Qian Xu, Nathan Nan Liu, Weizhu Chen, Wei Bi, Sinno Jialin Pan, Vincent Wenchen Zheng, Evan Wei Xiang, Weike Pan, Derek Hao Hu, Si Shen and Tengfei Liu.
%I would also like to thank Prof. Eric Xing for his insightful discussions and guidance on re- search during my visit to Carnegie Mellon University. My many friends helped me in many ways to adapt to life in the USA. They include Jun Zhu, Li Nao, Yanlin Li, Yin Zhang, Pingzhong Tang, Yuandong Tian, Lei Li, Junming Yin, Haiyi Zhu, Cao Shen, and Yu Sheng.
%Finally, I am deeply indebted to my family especially my mother whose love and support have been the source of my courage.